Supplementary Information

### 2020-11-28 doc/manuscript/MEE_manuscript_SI.Rmd
minor fixes

---
title: "Supplementary Information"
author:
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 3  
bibliography: references.bib
csl: global-change-biology.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

site_details_appendix_title<- "Appendix S1. Methods for reconstruction of $DBH$"
DBH_reconstruction_title <- "Appendix S2. Methods for reconstruction of $DBH$"
climate_correction_title <- "Appendix S3. Methods for climate data evaluation and correction"
traditional_comparison_title <- "Appendix S4.  Methods for comparing climwin results with traditional methods"
changing_climate_title <- "Appendix S5.  Dealing with rapidly changing climate and tree growth"

@@

\newpage
`r qualitative_results_comparison`, cont.
```{r eval = TRUE, echo=FALSE, warning=FALSE}
table_pt3 <- read.csv("tables_figures/qualitative_results_comparison.csv", 
                     colClasses=c("NULL", NA, NA, NA, NA, NA, NA), 
                     col.names=c("NULL", "species", "previously observed", "observed here", "previously observed", "observed here", "reference"), 
                     skip=breakrow2, nrows=breakrow3-breakrow2,
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt3, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  add_header_above(c(" ", "Precipitation response" = 2, "Temperature response" = 2)) %>%
  column_spec(2:5, width = col_width) %>%
  column_spec(6, width = "2cm") %>%
  pack_rows("Žofín Forest Dynamics Plot, Czech Republic", 1, 3, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Niobrara and Hansley, Nebraska, USA", 4, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("Scotty Creek, NW Territories, Canada", 13, 13, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 7) 
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @alfaro-sanchez_growth_2017; @vlam_temperature_2014; @helcoski_growing_2019; @maxwell_declining_2016; @aus_de_ar_tree_2018; @bumann_assessing_2019; @tumajer_increasing_2017; @sniderhan_growth_2016; @kaspar_species-specific_nodate
---
*Indicates results from a regional study including but not limited to cores from the focal site.

>>>>

---
title: "Supplementary Information"
author:
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: references.bib
csl: global-change-biology.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

site_details_appendix_title<- "Appendix S1. Site Details"
DBH_reconstruction_title <- "Appendix S2. Methods for reconstruction of $DBH$"
climate_correction_title <- "Appendix S3. Methods for climate data evaluation and correction"
traditional_comparison_title <- "Appendix S4.  Methods for comparing our approach with traditional methods"
changing_climate_title <- "Appendix S5.  Dealing with rapidly changing climate and tree growth"

@@

\newpage
`r qualitative_results_comparison`, cont.
```{r eval = TRUE, echo=FALSE, warning=FALSE}
table_pt3 <- read.csv("tables_figures/qualitative_results_comparison.csv", 
                     colClasses=c("NULL", NA, NA, NA, NA, NA, NA), 
                     col.names=c("NULL", "species", "previously observed", "observed here", "previously observed", "observed here", "reference"), 
                     skip=breakrow2, nrows=breakrow3-breakrow2,
                     stringsAsFactors = FALSE, check.names = FALSE)
kable(table_pt3, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  add_header_above(c(" ", "Precipitation response" = 2, "Temperature response" = 2)) %>%
  column_spec(2:5, width = col_width) %>%
  column_spec(6, width = "2cm") %>%
  pack_rows("Žofín Forest Dynamics Plot, Czech Republic", 1, 4, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Niobrara and Hansley, Nebraska, USA", 5, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  #pack_rows("Scotty Creek, NW Territories, Canada", 13, 13, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 7) 
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @alfaro-sanchez_growth_2017; @vlam_temperature_2014; @helcoski_growing_2019; @maxwell_declining_2016; @aus_de_ar_tree_2018; @bumann_assessing_2019; @tumajer_increasing_2017; @sniderhan_growth_2016; @kaspar_species-specific_nodate
---
*Indicates results from a regional study including but not limited to cores from the focal site.
